|

### 2023-01-30 paper.Rmd
autogit
Mon Jan 30 23:00:10 CET 2023: update-remote.sh

One important argument for using pre-training DAE-GP is that it might be a potential way to reduce the overall run-time of the algorithm by reducing the training time of each generations DAE-LSTM model. Especially in the context of optimization problems where solutions have to be found numerous times in a time efficient manner (e.g. Vehicle Routing in the Domain of Logistic Services), one major advantage of pre-training is that a pre-trained model can be re-used to optimize many instances of an optimization problem.

>>>>

One important argument for using pre-training with DAE-GP is that it might be a potential way to reduce the overall run-time of the algorithm by reducing the training time of each generation's DAE-LSTM model. Especially in the context of optimization problems where solutions have to be found numerous times in a time efficient manner (e.g. Vehicle Routing in the Domain of Logistic Services), one major advantage of pre-training is that a pre-trained model can be re-used to optimize many instances of an optimization problem.

Unfortunately, as shown in figure \@ref(fig:airfoil-runtime-total), for the experiment conducted on the airfoil dataset with 2 hidden layers a negative impact of pre-training can be observed for the DAE-GP runtime.
